Exploring Income Inequality Dynamics in Canada: A Geospatial and Temporal Analysis

### 2024-04-03 paper/paper.qmd
upload the pdf

This paper aims to delve into the intricate dynamics of income inequality within Canada, focusing on the period from 1976 to 2021. Leveraging a comprehensive dataset spanning multiple surveys, including the Survey of Consumer Finances (SCF), the Survey of Labour and Income Dynamics (SLID), and the Canadian Income Survey (CIS), we embark on a rigorous exploration of income trends across different provinces and over time. By examining key variables such as year, geographical location, income decile, and income range, we seek to uncover patterns and nuances in income distribution dynamics.

@@

```{r}
#| label: tbl-model1
#| tbl-cap: "Summary results for two models"
#| echo: false
#| eval: true
#| warning: false
#| message: false
first_model <- 
  readRDS(file = here::here("models/model2.rds"))

>>>>

This paper aims to investigate the intricate dynamics of income inequality within Canada, focusing on the period from 1976 to 2021. Leveraging a comprehensive dataset spanning multiple surveys, including the Survey of Consumer Finances (SCF), the Survey of Labour and Income Dynamics (SLID), and the Canadian Income Survey (CIS), we embark on a rigorous exploration of income trends across different provinces and over time. By examining key variables such as year, geographical location, income decile, and income range, we seek to uncover patterns and nuances in income distribution dynamics.

@@

```{r}
#| label: tbl-model1
#| tbl-cap: "Summary results for two models"
#| echo: false
#| eval: true
#| warning: false
